---
title: "ESM 207 Homework #2"
author: "Pat Byrne"
date: "4/20/2020"
output: html_document
---

```{r setup, include=FALSE}
# Clear global environment
rm(list = ls()) 
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

# Attach packages
library(tidyverse)
library(janitor)
library(stargazer)
library(ggthemes)
```


```{r}
# Lock and load in the data
data.df <- read_csv('HW2_Data.csv') 
```

```{r}
# Clean it
abate.df <- data.df %>% 
  pivot_longer(MC_A:MC_D, names_to = 'sector', values_to = 'MC') %>% 
  mutate(
    sector = case_when(
      sector == 'MC_A' ~ 'A',
      sector == 'MC_B' ~ 'B',
      sector == 'MC_C' ~ 'C',
      sector == 'MC_D' ~ 'D')) %>% 
  mutate(
    country = case_when(
      sector %in% c('A','B','C') ~ 'X',
      sector == 'D' ~ 'Y'))

# Cut it up
abate.A.df <- abate.df %>% 
  filter(sector == 'A')
abate.B.df <- abate.df %>% 
  filter(sector == 'B')
abate.C.df <- abate.df %>% 
  filter(sector == 'C')
abate.D.df <- abate.df %>% 
  filter(sector == 'D')
```

```{r}
# Take a look
ggplot(abate.df, aes(x = Abatement, y = MC, color = sector)) + 
  geom_line() 
```


```{r}
# Fit models
lm.A <- lm(formula = MC ~ Abatement, data = abate.A.df)

lm.B <- lm(formula = MC ~ I(Abatement^0.5), data = abate.B.df)

# Fit one just to the portion where it rises off of the x axis
abate.C.fit.df <- abate.C.df %>% 
  filter(Abatement > 30)
lm.C <- lm(formula = MC ~ Abatement, data = abate.C.fit.df)

lm.D <- lm(formula = MC ~ Abatement + I(Abatement^2), data = abate.D.df)
```

```{r}
# Calculate and store coefficient values
coef.A <- as.numeric(lm.A$coefficients) # Spot 1 is the intercept, spot 2 is coef
coef.B <- as.numeric(lm.B$coefficients) # spot 2 is coef for sqrt(x)
coef.C <- as.numeric(lm.C$coefficients)
coef.D <- as.numeric(lm.D$coefficients) # intercept, x, x2

# For equations of the form y = ax + b:
a.A <- coef.A[2]
b.A <- coef.A[1]
a.B <- coef.B[2]
b.B <- coef.B[1]
a.C <- coef.C[2]
b.C <- coef.C[1]

current.emissions <- c(170, 200, 230, 300)
```
A: 
MC-A = `r round(a.A,3)`x + `r round(b.A,3)`

MWTPollute-A = `r round(a.A,3)`(`r current.emissions[1]` - x) + `r round(b.A,3)`


B:
MC-B =`r round(a.B,3)`$\sqrt{x}$ + `r round(b.B,3)`

MWTPollute-B = `r round(a.B,3)`$\sqrt{}$(`r current.emissions[2]` - x) + `r round(b.B,3)`


C:
MC-C = `r round(a.C,3)`x + `r round(b.C,3)`

MWTPollute-C = `r round(a.C,3)`(`r current.emissions[3]` - x) + `r round(b.C,3)`


D:
MC-D = `r round(coef.D[3],3)`$x^2$ + `r round(coef.D[2],3)`$x$ + `r round(coef.D[1],3)`

MWTPollute-D = `r round(coef.D[3],3)`(`r current.emissions[4]` - $x$)$^2$ + `r round(coef.D[2],3)`(`r current.emissions[4]` - $x$) + `r round(coef.D[1],3)`
```{r}
# Compute simmed values 
abate.A.df <- abate.A.df %>% 
  mutate(
    estimated = a.A*Abatement + b.A
  ) 
  
abate.B.df <- abate.B.df %>% 
  mutate(
    estimated = a.B*sqrt(Abatement) + b.B
  ) 

abate.C.df <- abate.C.df %>% 
  mutate(
    estimated = a.C*Abatement + b.C
  ) 

abate.D.df <- abate.D.df %>% 
  mutate(
    estimated = coef.D[3]*(Abatement^2) + coef.D[2]*Abatement + coef.D[1]
  ) 

# Compute MWTPollute
# You can plot all of these using the demand curves I've created
emissions <- seq(0,250,5)
demand.A <- a.A*(current.emissions[1] - emissions) + b.A
demand.A.df <- tibble(emissions, demand.A)
demand.B <- a.B*sqrt(current.emissions[2] - emissions) + b.B
demand.B.df <- tibble(emissions, demand.B)
demand.C <- a.C*(current.emissions[3] - emissions) + b.C
demand.C.df <- tibble(emissions, demand.C)
demand.D <- coef.D[3]*(current.emissions[4] - emissions)^2 + coef.D[2]*(current.emissions[4] - emissions) + coef.D[1]
demand.D.df <- tibble(emissions, demand.D)
```

```{r}
# Plot the estimated supply alongside original points
ggplot(data = abate.A.df) +
  geom_line(aes(x = Abatement, y = estimated), color = 'red') + 
  geom_point(aes(x = Abatement, y = MC))

ggplot(data = abate.B.df) +
  geom_line(aes(x = Abatement, y = estimated), color = 'red') + 
  geom_point(aes(x = Abatement, y = MC))

ggplot(data = abate.C.df) +
  geom_line(aes(x = Abatement, y = estimated), color = 'red') + 
  geom_point(aes(x = Abatement, y = MC))

ggplot(data = abate.D.df) +
  geom_line(aes(x = Abatement, y = estimated), color = 'red') + 
  geom_point(aes(x = Abatement, y = MC))

ggplot() +
  geom_line(data = abate.A.df, aes(x = Abatement, y = estimated)) + 
  geom_line(data = abate.B.df, aes(x = Abatement, y = estimated), color = 'blue') +
  geom_line(data = abate.C.df, aes(x = Abatement, y = estimated), color = 'red') +
  geom_line(data = abate.D.df, aes(x = Abatement, y = estimated), color = 'green')
```


#### 3 
##### a - cap on carbon 
```{r}
# 2) Compute the cost to each sector
integrand.A <- function(x) {a.A*x + b.A}
integral.A <- integrate(integrand.A, 0, 100)
cost.A.a <- as.numeric(integral.A$value)

integrand.B <- function(x) {a.B*sqrt(x) + b.B}
integral.B <- integrate(integrand.B, 0, 100)
cost.B.a <- as.numeric(integral.B$value)

integrand.C <- function(x) {a.C*x + b.C}
integral.C <- integrate(integrand.C, 0, 100)
cost.C.a <- as.numeric(integral.C$value)

# 1) Compute the total cost
cost.countryX.a <- cost.A.a + cost.B.a + cost.C.a
```

##### b - tax
```{r}
# Computing the tax 
# We replace the MCAbatement with the tax - sectors will abate up to the point that doing so becomes more expensive than emitting
# Iterate this chunk with different taxes until A_total is at least 300
tax <- 54.35
A_A <- (tax - b.A)/a.A
A_B <- ((tax - b.B)/a.B)^2
A_C <- (tax - b.C)/a.C

# Total abatement - must be greater than 300 tons
A_total = A_A + A_B + A_C

# 2) Compute the cost to each sector
integrand.A <- function(x) {a.A*x + b.A}
integral.A <- integrate(integrand.A, 0, A_A)
cost.A.b <- as.numeric(integral.A$value) + (current.emissions[1] - A_A)*tax

integrand.B <- function(x) {a.B*sqrt(x) + b.B}
integral.B <- integrate(integrand.B, 0, A_B)
cost.B.b <- as.numeric(integral.B$value) + (current.emissions[2] - A_B)*tax

integrand.C <- function(x) {a.C*x + b.C}
integral.C <- integrate(integrand.C, 0, A_C)
cost.C.b <- as.numeric(integral.C$value) + (current.emissions[3] - A_C)*tax

# 3) Compute tax revenue
tax_revenue = ((current.emissions[1] - A_A) + (current.emissions[2] - A_B) + (current.emissions[3] - A_C))*tax

# 1) Compute the total cost
cost.countryX.b <- cost.A.b + cost.B.b + cost.C.b - tax_revenue
```


##### c - cap and trade
```{r}
# Derive an aggregate pollution demand curve equation
# Iterate this chunk with different MWTPs (MWTPollute) until Q_total is less than 300 tons
MWTP = 54.35
# -- Curve A -- Q_A = total pollution
# Original: MWTP = a.A*(Qo - Q_A) + b.A
Q_A = -(MWTP - b.A - a.A*current.emissions[1])/a.A 
# -- Curve B -- Q_B = total pollution
# Original: MWTP = a.B*sqrt(Qo - Q_B) + b.B
Q_B = -((MWTP - b.B)/a.B)^2 + current.emissions[2]
# -- Curve C -- Q_B = total pollution
# Original: MWTP = a.C*(Qo - Q_A) + b.C
Q_C = -(MWTP - b.C - a.C*current.emissions[3])/a.C 

# Total emissions - must be less than 300 tons
Q_total = Q_A + Q_B + Q_C

# 2) Compute the cost to each sector
integrand.A <- function(x) {a.A*x + b.A}
integral.A <- integrate(integrand.A, 0, (current.emissions[1] - Q_A))
cost.A.c <- as.numeric(integral.A$value)
cost.A.c <- cost.A.c - ((current.emissions[1] - 100) - Q_A)*MWTP

integrand.B <- function(x) {a.B*sqrt(x) + b.B}
integral.B <- integrate(integrand.B, 0, (current.emissions[2] - Q_B))
cost.B.c <- as.numeric(integral.B$value)
cost.B.c <- cost.B.c - ((current.emissions[2] - 100) - Q_B)*MWTP

integrand.C <- function(x) {a.C*x + b.C}
integral.C <- integrate(integrand.C, 0, (current.emissions[3] - Q_C))
cost.C.c <- as.numeric(integral.C$value)
cost.C.c <- cost.C.c - ((current.emissions[3] - 100) - Q_C)*MWTP

# 1) Compute the total cost
cost.countryX.c <- cost.A.c+ cost.B.c + cost.C.c
```

```{r}
# We're just going to repeat the same as in the chunk above but with Sector D and total allowable emissions of 600 tons
# Note that we're overwriting the variables from the previous chunk in this one because Pat is lazy - might have to change for 
# Iterate this chunk with different MWTPs (MWTPollute) until Q_total is less than 600 tons
MWTP = 37.6
# -- Curve A -- Q_A = total pollution
# Original: MWTP = a.A*(Qo - Q_A) + b.A
Q_A = -(MWTP - b.A - a.A*current.emissions[1])/a.A 
# -- Curve B -- Q_B = total pollution
# Original: MWTP = a.B*sqrt(Qo - Q_B) + b.B
Q_B = -((MWTP - b.B)/a.B)^2 + current.emissions[2]
# -- Curve C -- Q_B = total pollution
# Original: MWTP = a.C*(Qo - Q_A) + b.C
Q_C = -(MWTP - b.C - a.C*current.emissions[3])/a.C 
# Solved for Q_D with wolframalpha.com 
Q_D = 585*.5 - sqrt(250*MWTP - 937*.5)

# Total emissions - must be less than 600 tons
Q_total = Q_A + Q_B + Q_C + Q_D

AA = current.emissions[1] - Q_A
AB = current.emissions[2] - Q_B
AC = current.emissions[3] - Q_C
AD = current.emissions[4] - Q_D

integrand.A <- function(x) {a.A*x + b.A}
integral.A <- integrate(integrand.A, 0, (current.emissions[1] - Q_A))
cost.A.d <- as.numeric(integral.A$value)
cost.A.d <- cost.A.d - ((current.emissions[1] - 100) - Q_A)*MWTP

integrand.B <- function(x) {a.B*sqrt(x) + b.B}
integral.B <- integrate(integrand.B, 0, (current.emissions[2] - Q_B))
cost.B.d <- as.numeric(integral.B$value)
cost.B.d <- cost.B.d - ((current.emissions[2] - 100) - Q_B)*MWTP

integrand.C <- function(x) {a.C*x + b.C}
integral.C <- integrate(integrand.C, 0, (current.emissions[3] - Q_C))
cost.C.d <- as.numeric(integral.C$value)
cost.C.d <- cost.C.d - ((current.emissions[3] - 100) - Q_C)*MWTP

integrand.D <- function(x) {coef.D[3]*x^2 + coef.D[2]*x + coef.D[1]}
integral.D <- integrate(integrand.D, 0, (current.emissions[4] - Q_D))
cost.D.d <- as.numeric(integral.D$value)
cost.D.d <- cost.D.d - (300 - AA - AB - AC)*MWTP

# 1) Compute the total cost
cost.countries.d <- cost.A.d + cost.B.d + cost.C.d + cost.D.d
```








