---
title: "ESM 207 Homework #2"
author: "Pat Byrne"
date: "4/20/2020"
output: html_document
---

```{r setup, include=FALSE}
# Clear global environment
rm(list = ls()) 
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

# Attach packages
library(tidyverse)
library(janitor)
library(stargazer)
library(ggthemes)
```


```{r}
# Lock and load in the data
data.df <- read_csv('HW2_Data.csv') 
```

```{r}
# Clean it
abate.df <- data.df %>% 
  pivot_longer(MC_A:MC_D, names_to = 'sector', values_to = 'MC') %>% 
  mutate(
    sector = case_when(
      sector == 'MC_A' ~ 'A',
      sector == 'MC_B' ~ 'B',
      sector == 'MC_C' ~ 'C',
      sector == 'MC_D' ~ 'D')) %>% 
  mutate(
    country = case_when(
      sector %in% c('A','B','C') ~ 'X',
      sector == 'D' ~ 'Y'))

# Cut it up
abate.A.df <- abate.df %>% 
  filter(sector == 'A')
abate.B.df <- abate.df %>% 
  filter(sector == 'B')
abate.C.df <- abate.df %>% 
  filter(sector == 'C')
abate.D.df <- abate.df %>% 
  filter(sector == 'D')
```

```{r}
# Take a look
ggplot(abate.df, aes(x = Abatement, y = MC, color = sector)) + 
  geom_line() +
  facet_wrap(~sector)
```


```{r}
# Fit models
lm.A <- lm(formula = MC ~ Abatement, data = abate.A.df)

# lm.B.2 <- lm(formula = MC ~ Abatement, data = abate.B.df)
lm.B <- lm(formula = MC ~ I(Abatement^0.5), data = abate.B.df)

abate.C.fit.df <- abate.C.df %>% 
  filter(Abatement > 30)
lm.C <- lm(formula = MC ~ Abatement, data = abate.C.fit.df)

lm.D <- lm(formula = MC ~ Abatement + I(Abatement^2), data = abate.D.df)
#lm.D.2 <- lm(formula = MC ~ Abatement, data = abate.D.df)
```

```{r}
# Calculate and store coefficient values
coef.A <- as.numeric(lm.A$coefficients) # Spot 1 is the intercept, spot 2 is coef
coef.B <- as.numeric(lm.B$coefficients) # spot 2 is coef for sqrt(x)
coef.C <- as.numeric(lm.C$coefficients)
coef.D <- as.numeric(lm.D$coefficients) # intercept, x, x2

current.emissions <- c(170, 200, 230, 300)
```
A: 
MC-A = `r round(coef.A[2],3)`x + `r round(coef.A[1],3)`

MWTPollute-A = `r round(coef.A[2],3)`(`r current.emissions[1]` - x) + `r round(coef.A[1],3)`


B:
MC-B =`r round(coef.B[2],3)`$\sqrt{x}$ + `r round(coef.B[1],3)`

MWTPollute-B = `r round(coef.B[2],3)`$\sqrt{}$(`r current.emissions[2]` - x) + `r round(coef.B[1],3)`


C:
MC-C = `r round(coef.C[2],3)`x + `r round(coef.C[1],3)`

MWTPollute-C = `r round(coef.C[2],3)`(`r current.emissions[3]` - x) + `r round(coef.C[1],3)`


D:
MC-D = `r round(coef.D[3],3)`$x^2$ + `r round(coef.D[2],3)`$x$ + `r round(coef.D[1],3)`

MWTPollute-D = `r round(coef.D[3],3)`(`r current.emissions[4]` - $x$)$^2$ + `r round(coef.D[2],3)`(`r current.emissions[4]` - $x$) + `r round(coef.D[1],3)`
```{r}
# Compute simmed values, MWTPollute
abate.A.df <- abate.A.df %>% 
  mutate(
    estimated = coef.A[2]*Abatement + coef.A[1],
    demand = coef.A[2]*(current.emissions[1] - Abatement) + coef.A[1]
  ) 
  
abate.B.df <- abate.B.df %>% 
  mutate(
    estimated = coef.B[2]*sqrt(Abatement) + coef.B[1],
    demand = coef.B[2]*sqrt(current.emissions[2] - Abatement) + coef.B[1]
  ) 

abate.C.df <- abate.C.df %>% 
  mutate(
    estimated = coef.C[2]*Abatement + coef.C[1],
    demand = coef.C[2]*(current.emissions[3] - Abatement) + coef.C[1]
  ) 

abate.D.df <- abate.D.df %>% 
  mutate(
    estimated = coef.D[3]*(Abatement^2) + coef.D[2]*Abatement + coef.D[1],
    demand = coef.D[3]*((current.emissions[4] - Abatement)^2) + coef.D[2]*(current.emissions[4] - Abatement) + coef.D[1]
  ) 

# DF of simmed MCAbatement
abate.simmed.df <- tibble(abate.A.df$Abatement, abate.A.df$estimated, abate.B.df$estimated, abate.C.df$estimated, abate.D.df$estimated) 
  rename(abate.simmed.df, Abatement = `abate.A.df$Abatement`,  MC_A_e = `abate.A.df$estimated`, MC_B_e= `abate.B.df$estimated`, MC_C_e = `abate.C.df$estimated`, MC_D_e = `abate.D.df$estimated`)
```

```{r}
# Plot the estimated supply and demand alongside original points
ggplot(data = abate.A.df) +
  geom_line(aes(x = Abatement, y = estimated), color = 'red') + 
  geom_line(aes(x = Abatement, y = demand), color = 'blue') + 
  geom_point(aes(x = Abatement, y = MC))

ggplot(data = abate.B.df) +
  geom_line(aes(x = Abatement, y = estimated), color = 'red') + 
  geom_line(aes(x = Abatement, y = demand), color = 'blue') + 
  geom_point(aes(x = Abatement, y = MC))

ggplot(data = abate.C.df) +
  geom_line(aes(x = Abatement, y = estimated), color = 'red') + 
  geom_line(aes(x = Abatement, y = demand), color = 'blue') + 
  geom_point(aes(x = Abatement, y = MC))

ggplot(data = abate.D.df) +
  geom_line(aes(x = Abatement, y = estimated), color = 'red') + 
  geom_line(aes(x = Abatement, y = demand), color = 'blue') + 
  geom_point(aes(x = Abatement, y = MC))
```


#### 3 
##### a - cap on carbon 
```{r}
# 2) Compute the cost to each sector
integrand.A <- function(x) {coef.A[2]*x + coef.A[1]}
integral.A <- integrate(integrand.A, 0, 100)
cost.A.a <- as.numeric(integral.A$value)

integrand.B <- function(x) {coef.B[2]*sqrt(x) + coef.B[1]}
integral.B <- integrate(integrand.B, 0, 100)
cost.B.a <- as.numeric(integral.B$value)

integrand.C <- function(x) {coef.C[2]*x + coef.C[1]}
integral.C <- integrate(integrand.C, 0, 100)
cost.C.a <- as.numeric(integral.C$value)

# 1) Compute the total cost
cost.countryX.a <- cost.A.a + cost.B.a + cost.C.a

```

##### b - tax
```{r}
tax <- 54.35
A_A <- (tax - coef.A[1])/coef.A[2]
A_B <- ((tax - coef.B[1])/coef.B[2])^2
A_C <- (tax - coef.C[1])/coef.C[2]

A_total = A_A + A_B + A_C

# 2) Compute the cost to each sector
integrand.A <- function(x) {coef.A[2]*x + coef.A[1]}
integral.A <- integrate(integrand.A, 0, A_A)
cost.A.b <- as.numeric(integral.A$value)

integrand.B <- function(x) {coef.B[2]*sqrt(x) + coef.B[1]}
integral.B <- integrate(integrand.B, 0, A_B)
cost.B.b <- as.numeric(integral.B$value)

integrand.C <- function(x) {coef.C[2]*x + coef.C[1]}
integral.C <- integrate(integrand.C, 0, A_C)
cost.C.b <- as.numeric(integral.C$value)

# 1) Compute the total cost
cost.countryX.b <- cost.A.b + cost.B.b + cost.C.b

# 3) Compute tax revenue
tax_revenue = ((current.emissions[1] - A_A) + (current.emissions[2] - A_B) + (current.emissions[3] - A_C))*tax
```

##### c - cap and trade









