---
title: "ESM 207 Homework #2"
author: "Pat Byrne"
date: "4/20/2020"
output: html_document
---

```{r setup, include=FALSE}
# Clear global environment
rm(list = ls()) 
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

# Attach packages
library(tidyverse)
library(janitor)
library(stargazer)
library(ggthemes)
```


```{r}
# Lock and load in the data
data.df <- read_csv('HW2_Data.csv') 
```

```{r}
# Clean it
abate.df <- data.df %>% 
  pivot_longer(MC_A:MC_D, names_to = 'sector', values_to = 'MC') %>% 
  mutate(
    sector = case_when(
      sector == 'MC_A' ~ 'A',
      sector == 'MC_B' ~ 'B',
      sector == 'MC_C' ~ 'C',
      sector == 'MC_D' ~ 'D')) %>% 
  mutate(
    country = case_when(
      sector %in% c('A','B','C') ~ 'X',
      sector == 'D' ~ 'Y'))

# Cut it up
abate.A.df <- abate.df %>% 
  filter(sector == 'A')
abate.B.df <- abate.df %>% 
  filter(sector == 'B')
abate.C.df <- abate.df %>% 
  filter(sector == 'C')
abate.D.df <- abate.df %>% 
  filter(sector == 'D')
```

```{r}
# Take a look
ggplot(abate.df, aes(x = Abatement, y = MC, color = sector)) + 
  geom_line() +
  facet_wrap(~sector)
```


```{r}
# Fit models
lm.A <- lm(formula = MC ~ Abatement, data = abate.A.df)

# lm.B.2 <- lm(formula = MC ~ Abatement, data = abate.B.df)
lm.B <- lm(formula = MC ~ I(Abatement^0.5), data = abate.B.df)

abate.C.fit.df <- abate.C.df %>% 
  filter(Abatement > 30)
lm.C <- lm(formula = MC ~ Abatement, data = abate.C.fit.df)

lm.D <- lm(formula = MC ~ Abatement + I(Abatement^2), data = abate.D.df)
#lm.D.2 <- lm(formula = MC ~ Abatement, data = abate.D.df)
```

```{r}
# Calculate and store coefficient values
coef.A <- as.numeric(lm.A$coefficients) # Spot 1 is the intercept, spot 2 is coef
coef.B <- as.numeric(lm.B$coefficients) # spot 2 is coef for sqrt(x)
coef.C <- as.numeric(lm.C$coefficients)
coef.D <- as.numeric(lm.D$coefficients) # intercept, x, x2

current.emissions <- c(170, 200, 230, 300)
```
A: 
MC-A = `r round(coef.A[2],3)`x + `r round(coef.A[1],3)`

MWTPollute-A = `r round(coef.A[2],3)`(`r current.emissions[1]` - x) + `r round(coef.A[1],3)`


B:
MC-B =`r round(coef.B[2],3)`$\sqrt{x}$ + `r round(coef.B[1],3)`

MWTPollute-B = `r round(coef.B[2],3)`$\sqrt{}$(`r current.emissions[2]` - x) + `r round(coef.B[1],3)`


C:
MC-C = `r round(coef.C[2],3)`x + `r round(coef.C[1],3)`

MWTPollute-C = `r round(coef.C[2],3)`(`r current.emissions[3]` - x) + `r round(coef.C[1],3)`


D:
MC-D = `r round(coef.D[3],3)`$x^2$ + `r round(coef.D[2],3)`$x$ + `r round(coef.D[1],3)`

MWTPollute-D = `r round(coef.D[3],3)`(`r current.emissions[4]` - $x$)$^2$ + `r round(coef.D[2],3)`(`r current.emissions[4]` - $x$) + `r round(coef.D[1],3)`
```{r}
# Compute simmed values, MWTPollute
abate.A.df <- abate.A.df %>% 
  mutate(
    estimated = coef.A[2]*Abatement + coef.A[1]
  )

abate.B.df <- abate.df %>% 
  filter(sector == 'B')
abate.C.df <- abate.df %>% 
  filter(sector == 'C')
abate.D.df <- abate.df %>% 
  filter(sector == 'D')


```















