
```{r setup, include=FALSE}
# Clear global environment
rm(list = ls()) 
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

# Attach packages
library(tidyverse)
library(janitor)
library(stargazer)
library(ggthemes)
```


```{r}
# Lock and load in the data
data.df <- read_csv('HW2_Data.csv') 
```

```{r}
# Clean it
abate.df <- data.df %>% 
  pivot_longer(MC_A:MC_D, names_to = 'sector', values_to = 'MC') %>% 
  mutate(
    sector = case_when(
      sector == 'MC_A' ~ 'A',
      sector == 'MC_B' ~ 'B',
      sector == 'MC_C' ~ 'C',
      sector == 'MC_D' ~ 'D')) %>% 
  mutate(
    country = case_when(
      sector %in% c('A','B','C') ~ 'X',
      sector == 'D' ~ 'Y'))

# Cut it up
abate.A.df <- abate.df %>% 
  filter(sector == 'A')
abate.B.df <- abate.df %>% 
  filter(sector == 'B')
abate.C.df <- abate.df %>% 
  filter(sector == 'C')
abate.D.df <- abate.df %>% 
  filter(sector == 'D')
```

```{r, include = 'FALSE'}
# Take a look
ggplot(abate.df, aes(x = Abatement, y = MC, color = sector)) + 
  geom_line() 
```

## Appendix

This appendix contains supporting information describing the analytical approach used to answer questions 1-4. 

```{r}
# Fit models
lm.A <- lm(formula = MC ~ Abatement, data = abate.A.df)

lm.B <- lm(formula = MC ~ I(Abatement^0.5), data = abate.B.df)

# Fit one just to the portion where it rises off of the x axis
abate.C.fit.df <- abate.C.df %>% 
  filter(Abatement > 30)
lm.C <- lm(formula = MC ~ Abatement, data = abate.C.fit.df)

lm.D <- lm(formula = MC ~ Abatement + I(Abatement^2), data = abate.D.df)
```

```{r}
# Calculate and store coefficient values
coef.A <- as.numeric(lm.A$coefficients) # Spot 1 is the intercept, spot 2 is coef
coef.B <- as.numeric(lm.B$coefficients) # spot 2 is coef for sqrt(x)
coef.C <- as.numeric(lm.C$coefficients)
coef.D <- as.numeric(lm.D$coefficients) # intercept, x, x2

# For equations of the form y = ax + b:
a.A <- coef.A[2]
b.A <- coef.A[1]
a.B <- coef.B[2]
b.B <- coef.B[1]
a.C <- coef.C[2]
b.C <- coef.C[1]

current.emissions <- c(170, 200, 230, 300)
```

#### Question 1

A functional form for sector A would likely be y = mx + b. For sector B, which appears nonlinear, a functional form could be y = mx^1/2^ + c. For sector C, the marginal cost curve appears to be negative for values less than 30. Thus, the functional form could be estimated as y = mx + b as well. Finally, sector d appears to take the functional form of y = mx^2^ + bx + c. 

Using the lm() function, paramaters were calculated to find the equations for these abatement curves:

**Sector A:**

MC<sub>A</sub> = `r round(a.A,3)`x + `r round(b.A,3)`

**Sector B:**

MC<sub>B</sub> =`r round(a.B,3)`$\sqrt{x}$ + `r round(b.B,3)`

**Sector C:**

MC<sub>C</sub> = `r round(a.C,3)`x + `r round(b.C,3)`

**Sector D:**

MC<sub>D</sub> = `r round(coef.D[3],3)`$x^2$ + `r round(coef.D[2],3)`$x$ + `r round(coef.D[1],3)`

Each of these regressions was compared to regressions with other potential forms, with the regression resulting in the highest *r^2^* value being chosen as the most accurate. 

```{r}
# Compute simmed values 
abate.A.df <- abate.A.df %>% 
  mutate(
    estimated = a.A*Abatement + b.A
  ) 
  
abate.B.df <- abate.B.df %>% 
  mutate(
    estimated = a.B*sqrt(Abatement) + b.B
  ) 

abate.C.df <- abate.C.df %>% 
  mutate(
    estimated = a.C*Abatement + b.C
  ) 

abate.D.df <- abate.D.df %>% 
  mutate(
    estimated = coef.D[3]*(Abatement^2) + coef.D[2]*Abatement + coef.D[1]
  ) 

# Compute MWTPollute
# You can plot all of these using the demand curves I've created
emissions <- seq(0,250,5)
demand.A <- a.A*(current.emissions[1] - emissions) + b.A
demand.A.df <- tibble(emissions, demand.A)
demand.B <- a.B*sqrt(current.emissions[2] - emissions) + b.B
demand.B.df <- tibble(emissions, demand.B)
demand.C <- a.C*(current.emissions[3] - emissions) + b.C
demand.C.df <- tibble(emissions, demand.C)
demand.D <- coef.D[3]*(current.emissions[4] - emissions)^2 + coef.D[2]*(current.emissions[4] - emissions) + coef.D[1]
demand.D.df <- tibble(emissions, demand.D)
```

```{r, include = "FALSE"}
# Plot the estimated supply alongside original points
ggplot(data = abate.A.df) +
  geom_line(aes(x = Abatement, y = estimated), color = 'red') + 
  geom_point(aes(x = Abatement, y = MC))

ggplot(data = abate.B.df) +
  geom_line(aes(x = Abatement, y = estimated), color = 'red') + 
  geom_point(aes(x = Abatement, y = MC))

ggplot(data = abate.C.df) +
  geom_line(aes(x = Abatement, y = estimated), color = 'red') + 
  geom_point(aes(x = Abatement, y = MC))

ggplot(data = abate.D.df) +
  geom_line(aes(x = Abatement, y = estimated), color = 'red') + 
  geom_point(aes(x = Abatement, y = MC))

```

```{r}
ggplot() +
  geom_line(data = abate.A.df, aes(x = Abatement, y = estimated, color = 'darkorange')) + 
  geom_line(data = abate.B.df, aes(x = Abatement, y = estimated, color = 'blue')) +
  geom_line(data = abate.C.df, aes(x = Abatement, y = estimated, color = 'red')) +
  geom_line(data = abate.D.df, aes(x = Abatement, y = estimated, color = 'forestgreen')) +
  labs(x = "Abatement (t carbon)",
      y = "Price ($/t)",
      title = "Marginal Abatement Curves for Sectors A, B, C and D") +
  scale_color_identity(guide = "legend",
                       name = "Sector",
                       breaks = c("darkorange", "blue", "red", "forestgreen"),
                       labels = c("Sector A", "Sector B", "Sector C", "Sector D"))
  

```

#### Question 2 

The demand (or marginal willingess to pollute) curves for carbon pollution was derived from the abatement curves by substituting X = $Q_0$ - $Q$ into the abatement functions, using provided current emissions levels for each sector for $Q_0$.

**Sector A:** 

MC<sub>A</sub> = `r round(a.A,3)`x + `r round(b.A,3)`

MWTPollute<sub>A</sub> = `r round(a.A,3)`(`r current.emissions[1]` - x) + `r round(b.A,3)`

**Sector B:**

MC<sub>B</sub> =`r round(a.B,3)`$\sqrt{x}$ + `r round(b.B,3)`

MWTPollute<sub>B</sub> = `r round(a.B,3)`$\sqrt{}$(`r current.emissions[2]` - x) + `r round(b.B,3)`

**Sector C:**

MC<sub>C</sub> = `r round(a.C,3)`x + `r round(b.C,3)`

MWTPollute<sub>C</sub> = `r round(a.C,3)`(`r current.emissions[3]` - x) + `r round(b.C,3)`


**Sector D:**

MC<sub>D</sub> = `r round(coef.D[3],3)`$x^2$ + `r round(coef.D[2],3)`$x$ + `r round(coef.D[1],3)`

MWTPollute<sub>D</sub> = `r round(coef.D[3],3)`(`r current.emissions[4]` - $x$)$^2$ + `r round(coef.D[2],3)`(`r current.emissions[4]` - $x$) + `r round(coef.D[1],3)`

```{r}

ggplot() +
  geom_line(data = demand.A.df, aes(x = emissions, y = demand.A, color = 'darkorange')) +
  geom_line(data = demand.B.df, aes(x = emissions, y = demand.B, color = 'blue')) +
  geom_line(data = demand.C.df, aes(x = emissions, y = demand.C, color = 'red')) +
  geom_line(data = demand.D.df, aes(x = emissions, y = demand.D, color = 'forestgreen')) +
  labs(x = "Emissions (t carbon)",
      y = "Price ($/t)",
      title = "Marginal Emissions Demand Curves for Sectors A, B, C and D") +
  scale_color_identity(guide = "legend",
                       name = "Sector",
                       breaks = c("darkorange", "blue", "red", "forestgreen"),
                       labels = c("Sector A", "Sector B", "Sector C", "Sector D"))

```

#### Question 3 
##### a. Cap on Carbon
```{r}
# 2) Compute the cost to each sector
integrand.A <- function(x) {a.A*x + b.A}
integral.A <- integrate(integrand.A, 0, 100)
cost.A.a <- as.numeric(integral.A$value)

integrand.B <- function(x) {a.B*sqrt(x) + b.B}
integral.B <- integrate(integrand.B, 0, 100)
cost.B.a <- as.numeric(integral.B$value)

integrand.C <- function(x) {a.C*x + b.C}
integral.C <- integrate(integrand.C, 0, 100)
cost.C.a <- as.numeric(integral.C$value)

# 1) Compute the total cost
cost.countryX.a <- cost.A.a + cost.B.a + cost.C.a
```

A cap on carbon will reduce each sector's carbon emissions by 100 tons. To calculate the cost to each sector, the integral of the marginal supply curve was calculated for the interval (0, 100). The resulting cost to sector A is \$`r round(cost.A.a,2)`, the cost to sector B is  \$`r round(cost.B.a,2)`, and the cost to sector C is \$`r round(cost.C.a,2)`.

The total cost to country X from a cap on carbon was calculated by summing the cost of each sector. The total cost to country X is \$`r round(cost.countryX.a,2)`.

##### b. Tax

A properly calculated tax can achieve the same desired 300-ton reduction in emissions, not by limiting the sectors, but by taxing them so it will only be efficient to emit up to a certain level. To calculate the socially optimal tax, the tax was factored into each sector's abatement curve: 

Abatement<sub>A</sub> = (tax -`r round(b.A,3)`)/`r round(a.A,3)`

Abatement<sub>B</sub> = (tax - `r round(b.B,3)`)/`r round(a.B,3)`$^2$

Abatement<sub>C</sub> = (tax - `r round(b.C, 3)`)/`r round(a.C,3)`


```{r}
# Computing the tax 
# We replace the MCAbatement with the tax - sectors will abate up to the point that doing so becomes more expensive than emitting
# Iterate this chunk with different taxes until A_total is at least 300
tax <- 54.35
A_A <- (tax - b.A)/a.A
A_B <- ((tax - b.B)/a.B)^2
A_C <- (tax - b.C)/a.C

# Total abatement - must be greater than 300 tons
A_total = A_A + A_B + A_C

# 2) Compute the cost to each sector
integrand.A <- function(x) {a.A*x + b.A}
integral.A <- integrate(integrand.A, 0, A_A)
cost.A.b <- as.numeric(integral.A$value) + (current.emissions[1] - A_A)*tax

integrand.B <- function(x) {a.B*sqrt(x) + b.B}
integral.B <- integrate(integrand.B, 0, A_B)
cost.B.b <- as.numeric(integral.B$value) + (current.emissions[2] - A_B)*tax

integrand.C <- function(x) {a.C*x + b.C}
integral.C <- integrate(integrand.C, 0, A_C)
cost.C.b <- as.numeric(integral.C$value) + (current.emissions[3] - A_C)*tax

# 3) Compute tax revenue
tax_revenue = ((current.emissions[1] - A_A) + (current.emissions[2] - A_B) + (current.emissions[3] - A_C))*tax

# 1) Compute the total cost
cost.countryX.b <- cost.A.b + cost.B.b + cost.C.b - tax_revenue
```
The abatement for each sector was then summed together and the tax was altered until the total abatement for country X was 300 tons. The tax at this point was \$`r round(tax,2)`. The resulting cost to sector A is \$`r round(cost.A.b,2)`, the cost to sector B is \$`r round(cost.B.b,2)`, and the cost to sector C is \$`r round(cost.C.b,2)`.

The total tax revenue for country X was calculated by subtracting the abatement for each sector from the overall emissions at the socially optimal tax of \$`r round(tax,2)`. The tax revenue for country X is \$`r as.integer(tax_revenue)`.72.

The total cost to country X from a tax on carbon would be the sum of these costs less the country's tax revenue. The total cost to country X is \$`r round(cost.countryX.b,2)`. 

##### c. Cap and Trade

```{r}
# Derive an aggregate pollution demand curve equation
# Iterate this chunk with different MWTPs (MWTPollute) until Q_total is less than 300 tons
MWTP = 54.35
# -- Curve A -- Q_A = total pollution
# Original: MWTP = a.A*(Qo - Q_A) + b.A
Q_A = -(MWTP - b.A - a.A*current.emissions[1])/a.A 
# -- Curve B -- Q_B = total pollution
# Original: MWTP = a.B*sqrt(Qo - Q_B) + b.B
Q_B = -((MWTP - b.B)/a.B)^2 + current.emissions[2]
# -- Curve C -- Q_B = total pollution
# Original: MWTP = a.C*(Qo - Q_A) + b.C
Q_C = -(MWTP - b.C - a.C*current.emissions[3])/a.C 

# Total emissions - must be less than 300 tons
Q_total = Q_A + Q_B + Q_C

# 2) Compute the cost to each sector
integrand.A <- function(x) {a.A*x + b.A}
integral.A <- integrate(integrand.A, 0, (current.emissions[1] - Q_A))
cost.A.c <- as.numeric(integral.A$value)
cost.A.c <- cost.A.c - ((current.emissions[1] - 100) - Q_A)*MWTP

integrand.B <- function(x) {a.B*sqrt(x) + b.B}
integral.B <- integrate(integrand.B, 0, (current.emissions[2] - Q_B))
cost.B.c <- as.numeric(integral.B$value)
cost.B.c <- cost.B.c - ((current.emissions[2] - 100) - Q_B)*MWTP

integrand.C <- function(x) {a.C*x + b.C}
integral.C <- integrate(integrand.C, 0, (current.emissions[3] - Q_C))
cost.C.c <- as.numeric(integral.C$value)
cost.C.c <- cost.C.c - ((current.emissions[3] - 100) - Q_C)*MWTP

# 1) Compute the total cost
cost.countryX.c <- cost.A.c+ cost.B.c + cost.C.c
```

Cap and trade allows country X to set a cap on total carbon emissions and allow each sector 100 tons of emissions. These 100 credits can be traded among the sectors. A sector would do this if the market price of 1 ton of carbon credit is greater than their benefit of emitting that additional ton. To find that marginal willingness to pollute curves for each sector were rearranged for Q from the abatement function as follows: 

Q<sub>A</sub>= -(MWTP - `r round(b.A,3)` - `r round(a.A,3)`*`r (current.emissions[1])`)/`r round(a.A,3)` 

Q<sub>B</sub> = -((MWTP - `r round(b.B,3)`/`r round(a.B,3)`)$^2$ + `r current.emissions[2]`

Q<sub>C</sub> = -(MWTP - `r round(b.C,3)` - `r round(a.C,3)`*`r (current.emissions[3])`)/`r round(a.C,3)` 

Abatement for each sector was then summed together and the tax was altered until the total abatement for country X was 300 tons. This was at MWTP = \$`r round(MWTP,2)`. The resulting cost with cap and trade to sector A is \$`r round(cost.A.b,2)`, the cost to sector B is \$`r round(cost.B.b,2)`, and the cost to sector C is \$`r round(cost.C.b,2)`. The total cost to country X with cap and trade is \$`r round(cost.countryX.c,2)`.

#### Question 4

```{r}
# We're just going to repeat the same as in the chunk above but with Sector D and total allowable emissions of 600 tons
# Note that we're overwriting the variables from the previous chunk in this one because Pat is lazy - might have to change for 
# Iterate this chunk with different MWTPs (MWTPollute) until Q_total is less than 600 tons
MWTP_XY = 37.6
# -- Curve A -- Q_A = total pollution
# Original: MWTP = a.A*(Qo - Q_A) + b.A
Q_A = -(MWTP_XY - b.A - a.A*current.emissions[1])/a.A 
# -- Curve B -- Q_B = total pollution
# Original: MWTP = a.B*sqrt(Qo - Q_B) + b.B
Q_B = -((MWTP_XY - b.B)/a.B)^2 + current.emissions[2]
# -- Curve C -- Q_B = total pollution
# Original: MWTP = a.C*(Qo - Q_A) + b.C
Q_C = -(MWTP_XY - b.C - a.C*current.emissions[3])/a.C 
# Solved for Q_D with wolframalpha.com 
Q_D = 585*.5 - sqrt(250*MWTP_XY - 937*.5)

# Total emissions - must be less than 600 tons
Q_total = Q_A + Q_B + Q_C + Q_D

AA = current.emissions[1] - Q_A
AB = current.emissions[2] - Q_B
AC = current.emissions[3] - Q_C
AD = current.emissions[4] - Q_D

integrand.A <- function(x) {a.A*x + b.A}
integral.A <- integrate(integrand.A, 0, (current.emissions[1] - Q_A))
cost.A.d <- as.numeric(integral.A$value)
cost.A.d <- cost.A.d - ((current.emissions[1] - 100) - Q_A)*MWTP_XY

integrand.B <- function(x) {a.B*sqrt(x) + b.B}
integral.B <- integrate(integrand.B, 0, (current.emissions[2] - Q_B))
cost.B.d <- as.numeric(integral.B$value)
cost.B.d <- cost.B.d - ((current.emissions[2] - 100) - Q_B)*MWTP_XY

integrand.C <- function(x) {a.C*x + b.C}
integral.C <- integrate(integrand.C, 0, (current.emissions[3] - Q_C))
cost.C.d <- as.numeric(integral.C$value)
cost.C.d <- cost.C.d - ((current.emissions[3] - 100) - Q_C)*MWTP_XY

integrand.D <- function(x) {coef.D[3]*x^2 + coef.D[2]*x + coef.D[1]}
integral.D <- integrate(integrand.D, 0, (current.emissions[4] - Q_D))
cost.D.d <- as.numeric(integral.D$value)
cost.D.d <- cost.D.d - (300 - AA - AB - AC)*MWTP_XY

# 1) Compute the total cost
cost.countries.d <- cost.A.d + cost.B.d + cost.C.d + cost.D.d
```


To determine if it is beneficial for country Y to enter country X's carbon market. To calculate, sector D's abatement function was arranged for Q as was done for sectors A, B, and C in 3c above: 

Q<sub>D</sub> = 585*.5 - $\sqrt{(250*MWTP - 937*.5)}$

The abatement for sector D was summed with all sectors in country X and the MWTP was altered until total emissions reached 600 tons. The MWTP with both countries participating in the carbon market is \$`r (MWTP_XY)`. The cost to sector A is \$`r round(cost.A.d,2)`, the cost to sector B is \$`r round(cost.B.d,2)`, the cost to sector C is \$`r round(cost.C.d,2)`, and the cost to sector D is \$`r round(cost.D.d,2)`, meaning that they would gain money. The overall cost to countries X and Y is \$`r round(cost.countries.d,2)`.






